Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-10-23 thesis/paper_draft.qmd
minor refine scoring rules section

This section briefly introduces the scoring rules used to evaluate the point and probabilistic forecast accuracy in @sec-simulation and @sec-empirical.

For point forecasts, we use the mean squared error (MSE) to evaluate the accuracy of different reconciliation methods: $MSE = \frac{1}{n} \sum_{i=1}^n (y_{i, t+h} - \tilde{y}_{i,t+h|t})^2$, where $y_{i, t+h}$ is the realised value of series $i$ at time $t+h$, and $\tilde{y}_{i,t+h|t}$ is the reconciled point forecast.

@@

where $y_i$ is the observed value of $i$-th series, and $\boldsymbol{1}(.)$ is the indicator function. The Winkler score rewards narrow intervals that contain the observation, and penalises intervals that do not contain the observation.

@@

where $z_i = \frac{y_i - \mu_i}{\sigma_i}$, and $\Phi(.)$ and $\phi(.)$ are the CDF and probability density function (PDF) of a standard normal distribution, respectively.

@@

where $\boldsymbol{X}$ and $\boldsymbol{X}'$ are independent random vectors with multivariate distribution $F$, $\boldsymbol{y}$ is the observed vector, $||.||$ is the Euclidean norm, and $\beta \in (0, 2]$. We set $\beta = 1$ following common convention.

Since the closed-form expression of the ES may not available, we approximate it using Monte Carlo samples $\{\boldsymbol{x}_1, \ldots, \boldsymbol{x}_M\}$ drawn from $P$:

>>>>

This section summarises the scoring rules used to evaluate the point and probabilistic forecast accuracy in @sec-simulation and @sec-empirical.

For point forecasts, we use the mean squared error to evaluate the accuracy of different reconciliation methods: $MSE = \frac{1}{n} \sum_{i=1}^n (y_{i, t+h} - \tilde{y}_{i,t+h|t})^2$, where $y_{i, t+h}$ is the realised value of series $i$ at time $t+h$, and $\tilde{y}_{i,t+h|t}$ is the reconciled point forecast.

@@

where $y_i$ is the observed value of $i$-th series. The Winkler score rewards narrow intervals that contain the observation, and penalises intervals that do not contain the observation.

@@

where $z_i = \frac{y_i - \mu_i}{\sigma_i}$, and $\Phi(.)$ and $\phi(.)$ are the CDF and PDF (probability density function) of a standard normal distribution, respectively.

@@

where $\boldsymbol{X}$ and $\boldsymbol{X}'$ are independent random vectors having multivariate distribution $F$, $\boldsymbol{y}$ is the observed vector, $||.||$ is the Euclidean norm, and $\beta \in (0, 2]$. We set $\beta = 1$ following common convention.

Since the closed-form expression of the ES is not available, we approximate it using Monte Carlo samples $\{\boldsymbol{x}_1, \ldots, \boldsymbol{x}_M\}$ drawn from $F$:
